\begin{thebibliography}{9}
    
    \bibitem{RecoCognEmoELearnEnv}
    Berardina De Carolis, Francesca D’Errico, Nicola Macchiarulo, Marinella Paciello, and Giuseppe Palestra. 
    "Recognizing Cognitive Emotions in E-Learning Environment". In: 
    \textit{International Workshop on Higher Education Learning Methodologies and Technologies Online}. Springer, 2021, pp. 17--27.
    
    \bibitem{StudEngageFacialBehav}
    Paolo Buono, Berardina De Carolis, Francesca D'Errico, and Giuseppe Palestra.
    "Assessing student engagement from facial behavior in on-line learning."
    \textit{Journal Title} Volume, no. Number (2022): Pages.
    
    \bibitem{AFEWVAdatabaseInTheWild}
    Jean Kossaifi, Georgios Tzimiropoulos, Sinisa Todorovic, and Maja Pantic.
    AFEW-VA database for valence and arousal estimation in-the-wild.
    \textit{Image and Vision Computing}, 65:23--36, 2017. Elsevier.
    
    \bibitem{FacesOfEngagement}
    Jacob Whitehill, Zewelanji N Serpell, Yi-Ching Lin, Amy Foster, and Javier R Movellan. 
    "The Faces of Engagement: Automatic Recognition of Student Engagement from Facial Expressions." 
    \textit{IEEE Transactions on Affective Computing} 5, no. 1 (2014): 86--98.
    
    \bibitem{Livingstone}
    Richard Winn Livingstone.
    \textit{The future in education}. University Press, 1941.
    
    \bibitem{FacialCodingContinMonitor}
    S. Ceccaccia, A. Generosi, G. Cimini, S. Faggiano, L. Giraldi, and M. Mengoni, 
    ``Facial coding as a mean to enable continuous monitoring of student's behavior in e-Learning," in 
    \textit{Proceedings of the 2nd International Workshop on Higher Education Learning Methodologies and Technologies Online}, 2021, pp. 1--10.
    
    \bibitem{PredLocStudEngagInTheWild}
    Kardan, S., Kaghazgaran, M., Roshanfekr, P., Sayyad, A., Javidi, M. (2019). 
    Prediction and Localization of student engagement in the wild. Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition Workshops,
    year={2019}.
    
    \bibitem{PyFeat}
    Py-feat. (n.d.). Action Unit Reference. Retrieved from \url{https://py-feat.org/pages/au_reference.html}
    
    \bibitem{FacialExpresRecLocalBinaryPatt}
    Taheri, S.M., Daneshvar, S., Chen, Q. (2016). 
    Facial Expression Recognition Based on Local Binary Patterns and Kernel Discriminant Isomap. 
    Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition Workshops.
    
    \bibitem{StudEngagDataset}
    Student Engagement Dataset. Retrieved from 
    \url{https://www.kaggle.com/datasets/joyee19/studentengagement}

    \bibitem{DAiSEE}
    DAiSEE dataset. Retrived from \url{https://people.iith.ac.in/vineethnb/resources/daisee/index.html}

    \bibitem{FaceExpreRecoImgSeqTwoFoldRandomForestClass} X. Pu, K. Fan, X. Chen, L. Ji, and Z. Zhou, "Facial expression recognition from image sequences using twofold random forest classifier," \textit{Neurocomputing}, vol. 168, pp. 1173-1180, 2015. https://doi.org/10.1016/j.neucom.2015.05.005
    
    \bibitem{InferEmoFaceAUs} S. Velusamy, H. Kannan, B. Anand, A. Sharma, and B. Navathe, "A method to infer emotions from facial Action Units," in \textit{2011 IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP)}, Prague, Czech Republic, 2011, pp. 2028-2031. doi: 10.1109/ICASSP.2011.5946910.
    
    \bibitem{FaceEmoPredAUsDeepLearn} M. Nadeeshani, A. Jayaweera, and P. Samarasinghe, "Facial Emotion Prediction through Action Units and Deep Learning," in \textit{2020 2nd International Conference on Advancements in Computing (ICAC)}, Malabe, Sri Lanka, 2020, pp. 293-298. doi: 10.1109/ICAC51239.2020.9357138.
    
    \bibitem{LearnExpresSpatTempManiFoldDynamFaceExpressReco} M. Liu, S. Shan, R. Wang, and X. Chen, "Learning expressionlets on spatio-temporal manifold for dynamic facial expression recognition," in \textit{2014 IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}, 2014, pp. 1749-1756.
    
    \bibitem{RecoFaceExprMachLearnAppSpontBehav} M. S. Bartlett, G. Littlewort, M. Frank, C. Lainscsek, I. Fasel, and J. Movellan, "Recognizing facial expression: Machine learning and application to spontaneous behavior," in \textit{Proc. of IEEE Conf. on Compter Vision and Pat. Recog. (CVPR)}, 2005, pp. 568-573.
    
    \bibitem{AutoInfereComplMentStatesVid} R. el Kaliouby, "Mind-reading machines: the automated inference of complex mental states from video," Ph.D. Thesis, University of Cambridge, 2005.
    
    \bibitem{IntroToAlgo} T. H. Cormen, C. E. Leiserson, R. L. Rivest, and C. Stein, \textit{Introduction to algorithms}, 3rd ed., MIT Press, 2009.
    
    \bibitem{CUDA} \url{https://developer.nvidia.com/cuda-zone} 
    
    \bibitem{Tqdm} \url{https://tqdm.github.io/}
    
    \bibitem{OpenCv} Da \url{https://opencv.org/about/}
    
    \bibitem{scikitLearn} {https://en.wikipedia.org/wiki/Scikit-learn}
    
    \bibitem{Chen2018MobileFaceNets} S. Chen, Y. Liu, X. Gao, and Z. Han, "MobileFaceNets: Efficient CNNs for Accurate Real-time Face Verification on Mobile Devices," arXiv preprint arXiv:1804.07573, Apr. 2018.
    
    \bibitem{ChenG16}
    Tianqi Chen and Carlos Guestrin.
    \newblock XGBoost: {A} Scalable Tree Boosting System.
    \newblock {\em CoRR}, volume abs/1603.02754, 2016.
    \newblock \url{http://arxiv.org/abs/1603.02754}.
    
    \bibitem{FacialExprRecoUseResMaskNet}L. Pham, T. H. Vu and T. A. Tran, "Facial Expression Recognition Using Residual Masking Network," 2020 25th International Conference on Pattern Recognition (ICPR), Milan, Italy, 2021, pp. 4513-4519, doi: 10.1109/ICPR48806.2021.9411919.
    
    \bibitem{img2pose}V. Albiero, X. Chen, X. Yin, G. Pang and T. Hassner, "img2pose: Face Alignment and Detection via 6DoF, Face Pose Estimation," 2021 IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR), Nashville, TN, USA, 2021, pp. 7613-7623, doi: 10.1109/CVPR46437.2021.00753.
    
    \bibitem{radnomForestIbm} \url{https://www.ibm.com/topics/random-forest}
    
    \bibitem{KNNibm} \url{https://www.ibm.com/it-it/topics/knn}
    
    \bibitem{KNNEvelynFixJosephHodges} \url{https://apps.dtic.mil/sti/pdfs/ADA800276.pdf}
    
    \bibitem{NearNeighPattClass}T. Cover and P. Hart, "Nearest neighbor pattern classification," in IEEE Transactions on Information Theory, vol. 13, no. 1, pp. 21-27, January 1967, doi: 10.1109/TIT.1967.1053964.
    
    \bibitem{NaiveBayesClassTowardDataScience} \url{https://towardsdatascience.com/naive-bayes-classifier-81d512f50a7c}

    \bibitem{IncrLearnDailyRoutWorkflowSmartHomeEnvir} Carolis, Berardina De, Stefano Ferilli and Domenico Redavid. “Incremental Learning of Daily Routines as Workflows in a Smart Home Environment.” ACM Transactions on Interactive Intelligent Systems (TiiS) 4 (2015): 1 - 23.

    \bibitem{WoMan}S. Ferilli, "WoMan: Logic-Based Workflow Learning and Management," in IEEE Transactions on Systems, Man, and Cybernetics: Systems, vol. 44, no. 6, pp. 744-756, June 2014, doi: 10.1109/TSMC.2013.2273310.

    \bibitem{CohnKanadeDatabase} \url{https://www.ri.cmu.edu/project/cohn-kanade-au-coded-facial-expression-database/}

    \bibitem{OuluCasia} \url{https://paperswithcode.com/dataset/oulu-casia}

    \bibitem{BelfastInducedNaturalEmotionDatabase}I. Sneddon, M. McRorie, G. McKeown and J. Hanratty, "The Belfast Induced Natural Emotion Database," in IEEE Transactions on Affective Computing, vol. 3, no. 1, pp. 32-41, Jan.-March 2012, doi: 10.1109/T-AFFC.2011.26.
    
\end{thebibliography}
